---
title: "Assignment 1: R Markdown practice"
author: "Sam Ritter"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    smart: true
    dev: svg
urlcolor: blue
---

<!-- Write your Markdown below this line -->

#  How the Course Works

The weekly interactive tutorials must be completed by the start of each week. Then each weekly
assignment will be due at the end of the week.

# Course Goals

By the end of the course, students will be able to:

*  Use GitHub for creating a reproducible research document.
    * My GitHub username is: write_your_github_username_here_in_italic_text.
    
* Obtain, clean, transform, and visualize a dataset using the R programming language.

* Interpret and predict dataset trends using statistical inference and models.

* Critically examine and interpret statistical claims reported in mass media

# Including Code

## Running R code in code chunk

```{r}
x <- 2 + 4
x + 9
```

The output of first line of code is not printed out because it is assigned to a variable instead.

The second line of output is printed out instead, but this means that the calculated value has not
been saved for future use.

##  Displaying Graphs

```{r}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width)
```






